### 2020-09-09 LaTeX/sections/paper.tex
Edits

% = = = = = = = = = = = = = = = = =
\subsection*{Contributions.}

@@

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exception is in the case of a tie on price, which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

% With 50 selfdestructs

\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways. We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract). Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller. Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list. Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results in the less final net cost due to the 24000 gas refunds. Also, it is best to avoid storing unnecessary storage variables on chain. Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing highest priority elements in the two implementations of sorted linked lists that contain 50 unsigned integers.

\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways. For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded~\cite{wood2014ethereum}. So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction. In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority item and not delete the mapping element associated with the previous pointers. As it can be seen in the last two columns of Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas for dequeuing 50 unsigned integers compared to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.

 that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list. In

% = = = = = = = = = = = = = Experimentations = = = = = = = = = = = = = = = = = = =  %

@@

In this research work, we design and implement a call market on the Ethereum blockchain. We divide the trading day into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages. These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other. Our proposed decentralized exchange is both data structure and token agnostic (traders can trade ERC20 standard compliant token). The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.

As mentioned in~\ref{sec:callmarket}, Our system treats the time as discrete and not continuous; upcoming orders are accumulated over predetermined time intervals and are processed in batch instead of serially in order of receipt. The trading day is divided into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages. These orders are accumulated in a linked list with mapping priority queue and when the trading period is over, orders are matched against each other. The call market smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI, Table~\ref{tab:callmarket_functions} represents the call market's primary operations.

%GitHub repo:  \footnote{\CallMarketRepo}
% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
\begin{table}[]
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline

@@

To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods. The collateralized call market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.

Followings outline results of the experiments we performed using Javascript and leveraging Mocha testing framework.

%============= Worst_Case_Matching_test.js Tables=================== %

 \subsection{Experiments}

Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market. We used three different designs of the linked list with mapping priority queue. (1) Every time a trade happens, we use the \texttt{DELETE} method to remove the mapping elements that contains best bid and ask orders from storage completely \textbf{and} update the head and tail pointers of the list. (2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process. Instead we destroy the priority queue smart contract~\footnote{We execute a public function defined in the priority queue smart contract which itself calls the \texttt{self-destruct()} operation and transfers its funds (if any) to the call market contract.} once the matching is completed. (3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data. As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operation shows a better performance when killing the priority contract and/or not clearing data from the chain. However, leaving unnecessary storage data on chain is not a proper design practice (note that as mentioned in Section~\ref{sec:LLvsLLMapping}, destroying a smart contract does not remove the initial byte code of the contract from the chain but it frees up the state storage and refunds 24000 gas to the caller.)
The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).

Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.

%Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost. So it can still match as same number of orders (before running out of gas) as in the no on chain clearing implementation.

% = = = = = = = = = = = =Worst Case Matching on Linkedlist With Mapping Table = = = = = = = = = = = = =  %

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{\thead{Linked List with Mapping}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}}    \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Clearing the Mapping Elements}}         			& 86 pairs                					& 5,433,259                   				& 62,774,170                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{}
\label{tab:LLMApping_worst_case_matching}}
\end{table}

% = = = = = = = = = = = =Worst_Case_Matching Table = = = = = = = = = = = = =  %

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 38 pairs                & 5,372,679                   	& 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 42 pairs                & 5,247,636                  	& 333,656,805                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 46 pairs                & 5,285,275                     & 226,499,722                        \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linkedlist}                       							& 152 pairs                & 5,495,265                     & 35,823,601                        \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 86 pairs                 & 5,433,259                     & 62,774,170                        \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{}
\label{tab:worst_case_matching}}
\end{table}

@@

@@

@@

% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
\label{tab:PQUnitTests}}
\end{table}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %

\end{tabular}
\caption{\footnotesize{}
\label{tab:LLvsLLMapping}}
\end{table}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

>>>>

% = = = = = = = = = = = = = = = = =
\subsection*{Contributions.}
Our design \cm is intended as a simple module that developers can modify as they choose. By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges. The main advantage of blockchain is low barriers of entry and this further lowers the barrier.

@@

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

%Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.

One consequence of a linked list is that a new contract is created for every node in the list. Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.'). However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{dequeue()} function. As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.  This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds. Unfortunately, this is not universally true as shown by applying the same principle to the Linked List with Mapping.

Dequeuing in a linked list with mapping can be implemented in two ways. The simplest approach is process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again). Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}. As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper then cleaning it up.

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and cleanup to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select Linked List with Mapping and \texttt{DELETE} for \cm.

% = = = = = = = = = = = = = Implementatiion = = = = = = = = = = = = = = = = = = =  %

@@

%GitHub repo:  \footnote{\CallMarketRepo}
% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
\begin{table}[t]
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline

@@

Our design \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept orders. Orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). This is akin to how a crossing network operates in traditional finance (\ie \textblue{some explanation}). We keep the design simple by not allowing cancellations. Because markets are relatively short-lived, cancelations require a second transaction (and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}), orders simply expire when the market call period ends.

Another simplifying assumption was to implement a \textit{collateralized} call market. We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes. We revisit alternatives to this design below. This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).

% Volume of 1
% Ties?

\cm is written in 225 lines (SLOC) of Solidity (including 3 external libraries),\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}. We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics. Table~\ref{tab:callmarket_functions} represents the call market's primary operations.

%============= Performance =================== %

 \subsection{Performance}

 \input{tables/performance.tex}

The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, \textblue{using Ethereum today}. As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determined the highest number of orders that can be processed in a single call to \texttt{CloseMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost to the trader of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

As expected, the numbers closely track the performance of the PQ itself suggesting the PQ is indeed the main influence on performance. In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction. If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed. The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum comes with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second). That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences. \cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).

\textblue{Optimize for closing market, even at cost of higher submission.}

@@

% Cancelations
% How quick we open and close
%

@@

% Safely returning collateral 
% Options for non-collaterialized markets

@@

%
%% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
%
%\begin{table}[]
%\centering
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%
%\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%
%\end{tabular}
%\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
%\label{tab:PQUnitTests}}
%\end{table}
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%\begin{table}[]
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%
%\end{tabular}
%\caption{\footnotesize{}
%\label{tab:LLvsLLMapping}}
%\end{table}
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
